Describe and Explore: Using feature-based time series clustering to identify meaningful structures in intensive longitudinal data

### 2023-01-02 manuscript.tex
:pencil: intro str

Time series clustering has a number of conceptual use cases with psychological data. Prime among them is the ability to reduce the time, variable, and person complexity by extracting participant-level structures. These reduction and structuring qualities can be essential in detecting phenomena and extracting more abstract functional principles \citep[][]{eronen2021a}. These phenomena and principles can be meaningful differences that distinguish participants in different clusters, as well important patterns, trends, and relationships that participants share within a cluster \citep[e.g.,][]{schrodt2000}. Once distinct groups and patterns have been identified, researchers can examine the extent to which these within-group and between-group structures are associated with other variables of interest, such as personality traits, demographic characteristics, or other psychological constructs \citep[e.g.,][]{monden2022}. Once meaningful and robust structures and patterns are detected, time series clustering can, thus, be used to inform the development of robust theories as well as targeted interventions and therapies for individuals, for example, with mood disorders and other psychological conditions \citep[e.g.,][]{borsboom2021, eronen2020}.

@@

>>>>

Time series clustering has a number of conceptual use cases with psychological data. Prime among them is the ability to reduce the time, variable, and person complexity by extracting and organizing participant-level structures. These reduction and structuring qualities can be essential in detecting phenomena and extracting more abstract functional principles \citep[][]{eronen2021a}. These phenomena and principles can be meaningful differences that distinguish participants in different clusters, as well important patterns, trends, and relationships that participants share within a cluster \citep[e.g.,][]{schrodt2000}. Once distinct groups and patterns have been identified, researchers can examine the extent to which these within-group and between-group structures are associated with other variables of interest, such as personality traits, demographic characteristics, or other psychological constructs \citep[e.g.,][]{monden2022}. Once meaningful and robust structures and patterns are detected, time series clustering can, thus, be used to inform the development of robust theories as well as targeted interventions and therapies for individuals, for example, with mood disorders and other psychological conditions \citep[e.g.,][]{borsboom2021, eronen2020}.

@@

However, while clustering can be incredibly useful, arriving at these clusters critically depends on two core challenges.

this means time series clustering critically depends on making time series comparable to 
identify key (dis)similarities and then accurately distinguishing different groups \citep[e.g.,][]{Aghabozorgi2015}.
